Risk Perceptions for Wearable Devices

### 2015-02-20 results.tex
cleanup

% THIS IS SIGPROC-SP.TEX - VERSION 3.1
% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
% APRIL 2009
%
% It is an example file showing how to use the 'acm_proc_article-sp.cls' V3.2SP
% LaTeX2e document class file for Conference Proceedings submissions.
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls V3.2SP) *DOES NOT* produce:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line with ACM data
%       4) Page numbering
% ---------------------------------------------------------------------------------------------------------------
% It is an example which *does* use the .bib file (from which the .bbl file
% is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission,
% you need to 'insert'  your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%
% Questions regarding SIGS should be sent to
% Adrienne Griscti ---> griscti@acm.org
%
% Questions/suggestions regarding the guidelines, .tex and .cls files, etc. to
% Gerald Murray ---> murray@hq.acm.org
%
% For tracking purposes - this is V3.1SP - APRIL 2009

\documentclass{acm_proc_article-sp}

\usepackage{color}

%%% still need to break urls

\usepackage[hyphens]{url}

\def\etal{{\it et al.~}}

\newenvironment{packed_enum}{
\begin{enumerate}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
}{\end{enumerate}}

\newenvironment{packed_item}{
\begin{itemize}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
}{\end{itemize}}

\begin{document}

\title{Risk Perceptions for Wearable Devices}
%\titlenote{(Does NOT produce the permission block, copyright information nor page numbering). For use with ACM\_PROC\_ARTICLE-SP.CLS. Supported by ACM.}}

%\subtitle{[Extended Abstract]
%\titlenote{Note
%\textit{Note \LaTeX$2_\epsilon$\ and BibTeX} at \texttt{www.website.com}}}

%\numberofauthors{1}
%\author{
% \alignauthor Linda N. Lee\textsuperscript{1}, Serge Egelman\textsuperscript{1,3}, Joong Hwa Lee\textsuperscript{2}, David Wagner\textsuperscript{1}\\
%   \vspace{0.5em}
%   \affaddr{\textsuperscript{1}University of California, Berkeley, \{lnl,egelman,daw\}@cs.berkeley.edu}, \textsuperscript{2}dlwndghk94@berkeley.edu\\
%   \affaddr{\textsuperscript{3}International Computer Science Institute, egelman@icsi.berkeley.edu}\\
%}

\numberofauthors{1}
\author{
 \alignauthor Anonymous\\
   \vspace{0.5em}
   \affaddr{Some Place}
}

\maketitle
\begin{abstract}
We performed an online survey to examine risk perceptions surrounding wearable computing devices. We examine different data types that might be captured,  and the effect of who the data is shared with. We surveyed 1,784 participants about 88 data types and 4 data recipients to quantify risk perceptions across a wide range of scenarios, and evaluate of which factors contribute to the severity of these risks. Following previous work, we also asked participants to perform a risk/benefit analysis of 20 new technologies along with other well-understood technologies. The results of this study can be used to guide future research in wearable device security, especially research that helps protect sensitive data and design effective privacy notifications or indicators.
\end{abstract}

% A category with the (minimum) three required fields
\category{K.6.5.}{Management of Computing and Information Systems}{Security and protection}[Unauthorized access]

%\terms{Human Factors}{Measurement}{Security}

\keywords{Privacy, Security, User Studies, Risk Perception, Ubiquitous Computing, Wearable Devices} % NOT required for Proceedings

%%%%%%%%%%%%%%%%%%%
%%%         PAPER BODY         %%%
%%%%%%%%%%%%%%%%%%%

\section{Introduction}
With their ability to constantly capture data and help users, wearable devices, or ``wearables,'' are the new frontier of ubiquitous computing. Wearable technology has many potential benefits, ranging from a more natural, human-centered interface for computing, to healthier living through fitness tracking. Forbes has named 2014 the ``Year of Wearable Technology''~\cite{Forbes}, and a top 25 market research company estimates that 52\% of technology consumers are aware of wearables and 33\% said they were likely to buy one~\cite{NPD}.

The market for wearable devices is currently in infancy. It is hard to predict what device and applications will be most popular, but we use the current interest as a baseline. A survey of 3,956 respondents with high interest in wearables found that, currently, the most popular devices are fitness bands (61\%), followed by smart watches (45\%) and mobile health devices (17\%)~\cite{Nilsen}. It is estimated that 20\% of the general population owns at least one wearable and 10\% use at least one in their daily lives~\cite{WearableStatNews}. Most wearables consumers are young (48\% are between 18 and 34), but this \$700 million industry will reach other demographics soon~\cite{cmo}.

Wearable devices bring with them new potential security and privacy concerns. Many concerns exposure of users' activities without their awareness or consent. For instance, Fitbit's fitness profiles were public by default and also allowed sex to be tracked as exercise~\cite{Fitbit}, resulting in the inadvertent disclosure of sensitive information. Additionally, public discomfort prevented companies from enabling capabilities; Google Glass apps are prohibited from using facial recognition to mitigate potential privacy concerns~\cite{GlassDetection}.

To avoid scandalous breaches of privacy and public opposition to new capabilities, it is critical we understand user concerns surrounding wearable devices before wearables become increasingly powerful and ubiquitous~\cite{Implants}. A better understanding of users' risk perceptions will enable researchers and companies to focus on users' concerns. The goal of this paper is to gain a better sense of what those concerns are.

We surveyed 1,784 Internet users for their perceptions of wearable devices. In this work, we contribute the following: \\[-0.8cm]

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item We compare users' perceptions of a range of privacy and security risks of wearables. Users care much more about the type of data, than the recipient of the data.
\item We observed that users make little distinction between sharing data with friends, co-workers, or the general public, but are relatively comfortable with an application's servers receiving their data.
\item Our participants viewed data-collection capabilities of wearable devices as benign compared to more familiar technologies. However, we suspect that this may be due to a lack of exposure to these newer technologies.
%\item We report people's self-reported top concerns for wearable devices. Privacy, by far, is the top concern. Other notable risks include information security, long-term health risks from use, high financial cost, and change in social norms. 
\end{itemize}

%%%%%%%%%%%%%%%%%%%

\section{Methodology}

Our survey contained two main sections.
In one section, we presented participants with several scenarios---something undesirable that might happen with their wearable device---and asked them to rate their level of concern if each scenario were to happen.
This was intended to elicit their perception of the severity and impact of the risk.
In the other section, we asked participants to compare the risks and benefits of wearable technologies to better understood technologies, following the same methodology as a seminal study in risk perception by Fischhoff \etal \cite{Fischhoff}.
Our survey design is based on two prior perception studies, as we describe next.

%Finally, we collected demographic information, which included a privacy concern scale and whether participants owned any wearable devices.

%LL: this commented out for anonymity; can comment back in later.
%%% The full survey can be found at http://www.surveygizmo.com/s3/1657924 /Wearables-Threats-User-Survey.

%::LL: David, I spliced the related work; the text related to work directly related to our research to introduce/motivate the methodology remains here. The rest were put at the end of the paper, as you requested.

\subsection{Methodology Motivation}
\subsubsection{Smartphone Risk Scenarios}
Felt \etal previously studied the security concerns of smartphone users by conducting a large-scale online survey~\cite{Felt}. Their survey asked 3,115 smartphone users about 99 risk scenarios. Participants were asked how upset they would be if a certain action had occurred without permission. Participants rated each situation on a Likert scale ranging from ``indifferent (1)'' to ``very upset (5).''
Our methodology closely follows that study, but with different scenarios chosen to shed light on security and privacy risks of wearable devices.

\subsubsection{Technology Risk Perception}
Fischhoff \etal performed a seminal study of perceived risks with 30 widely used technologies~\cite{Fischhoff}. In their study, participants were asked to separately rate the risks and benefits for those technologies. They were told to think about all people affected by the technology, and to think about long-term vs. short-term risks and benefits. Then, the participants rated these technologies with respect to each other on a numerical scale, being instructed to rate the least risky or least beneficial technology a 10 and scaling the ratings linearly (e.g., a technology with risk rating 20 is considered twice as risky compared to a technology with a risk rating of 10).
We apply their methodology to evaluate perceived risks and benefits of several technologies related to wearable computing.

%Using this methodlogy, they were able to categorize different technologies based on whether they were high-risk/high-benefit, low-risk/low-benefit, and so forth.

\subsection{Survey Questions}
In our survey, each participant answered 27 questions, across five different sections:   \\[-.8cm]

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item 2 comprehension questions
\item 6 questions about wearable computing scenarios 
\item 2 questions about smartphone scenarios 
\item 2 risk/benefit questions 
\item 15 demographic questions \\[-.8cm]
\end{itemize}

We randomized the order participants saw sections of the survey (with the exception of the comprehension and demographic questions, which were always first and last, respectively), as well as the order of questions in each section.

\subsubsection{Comprehension Questions}
Because participants might be biased to specific companies (e.g., visceral reactions to Google Glass based on popular media stories), we based our questions on a fictitious wearable. Thus, the beginning of the survey introduced participants to the ``Cubetastic3000,'' which was the basis for all questions on wearables risks. We highlighted the capabilities of this device and described use cases. To ensure that participants had read and understood this device's capabilities, we ask them two multiple-choice comprehension questions.

\subsubsection{Wearables Scenarios}
We presented scenarios involving data capture using the Cubetastic3000 and asked them to rate how upset they would be if a particular data type (e.g., video, audio, gestures, etc.) were shared with a particular data recipient without asking first (see Figure \ref{fig:prompt}). Responses were collected on a 5-point Likert scale (from ``indifferent'' to ``very upset''), which was modeled after Felt et al.'s study of smartphone users' risk perceptions~\cite{Felt}. Our questions were of the format:

\textit{``How would you feel if an app on your Cubetastic3000 learned <data> and shared it with <recipient>, without asking you first?''}.

We created an initial pool of 288 questions by combining 72 data types (<data>) with 4 data recipients (<recipient>). The 4 possible data recipients were: \\[-.8cm]

\begin{figure}[t]
	\centering
	\includegraphics[width=0.47\textwidth]{prompt.pdf}
	\caption{An example of a wearable scenario question participants saw while taking the survey.}
	\label{fig:prompt}
\end{figure}

\begin{packed_item}
\item Your work contacts
\item Your friends
\item The public
\item The app's server (but didn't share it with anyone else)\\[-.8cm]
\end{packed_item}

The purpose of these questions was to determine the extent data types and data recipients play a role in upsetting participants when data is inappropriately shared. Additionally, we added 16 questions about other misbehaviors that did not follow this format, lacking either <data> or a <recipient>, but we found relevant nonetheless. An example of one of these questions was, ``\textit{How would you feel if an app on your Cubetastic3000 turned your device off, without asking you first?}'' There were a total of 304 questions in this set, from which we randomly 6 questions for each participant.

\subsubsection{Smartphone Scenarios}
\label{sec:smartphones}
We presented participants with a second set of scenarios to control for the type of device being used. These questions followed the format of the previous question set, but substituted ``smartphone'' for ``Cubetastic3000.'' Rather than using the previous pool of 288 <data> and <recipient> combinations, we selected 5 of the scenarios that Felt \etal found least and most concerning to their participants~\cite{Felt}. We randomly presented each participant with 2 of these 5 questions: \\[-.8cm]

\begin{packed_enum}
\item \textit{How would you feel if an app on your smartphone vibrated your phone without asking you first?}
\item \textit{How would you feel if an app on your smartphone connected to a Bluetooth device (like a headset) without asking you first?}
\item \textit{How would you feel if an app on your smartphone un-muted a phone call without asking you first?}
\item \textit{How would you feel if an app on your smartphone took screenshots when you were using other apps, without asking you first?}
\item \textit{How would you feel if an app on your smartphone sent premium (they cost money) calls or text messages, without asking you first?} 
\end{packed_enum}

\subsubsection{Risk and Benefit Assessment}
In addition to investigating reactions to particular scenarios, we examined broad perceptions of new technologies and how those compared to perceptions of other understood technologies. We modeled this section after a seminal risk perception study by Fischhoff \etal\cite{Fischhoff}, in which participants ranked technologies by their relative risk and benefit to society. We asked participants to perform this exercise for 4 technologies previously examined by Fischhoff {\it et al.}: handguns, motorcycles, lawnmowers, and electricity, which were chosen to span varying levels of risks and benefits.

Alongside the 4 studied technologies, we asked participants to evaluate one of 20 technologies relevant to wearables: internet, email, laptops, smartphones, smart watches, fitness trackers, Google Glass, Cubetastic3000, discrete camera, discrete microphone, facial recognition, facial detection, voice recognition, voice-based emotion detection, location tracking, speech-to-text, language detection, heart rate detection, age detection, and gender detection. We asked about familiar technologies such as the internet, general and specific wearable artifacts, and a range of new capabilities.

%LL: we didn't pick it because they were studied by this study, so this is a bit distracting, especially since the related work is at the end instead of before this.. 
%Many of these technologies were selected from those studied by Egelman \etal\cite{Egelman2015}.

To parallel Fischhoff {\it et al.}'s risk perception study, we gave our participants a similar prompt to numerically express the perceived gross risk/gross benefit over a long period of time for all parties involved. We randomized whether they performed the ranking for risks or benefits first. The prompt is listed in Appendix \ref{sec:prompt}. The question format was as follows:

\textit{Fill in your <risk/benefit> numbers for the following:}\\[-.5cm]

\textit{Handguns}: \_\_\_\_\_\_\_ \\
\textit{Motorcycles}: \_\_\_\_\_\_\_\\
\textit{Lawnmowers}: \_\_\_\_\_\_\_\\
\textit{<Wearable Technology>}: \_\_\_\_\_\_\_\\
\textit{Electricity}: \_\_\_\_\_\_\_\\ [-.5cm]

\subsubsection{Additional Questions}
The exit portion of the survey firstly consisted of questions asking for age, gender, and education. Then, we asked participants if they owned a wearable device so we could control for prior exposure, and included an open-ended question on what would be the most likely risks associated with wearable devices. We end with the 10-question Internet Users' Information Privacy Concerns (IUIPC) index~\cite{malhotra2004internet}, so we could control for participants' general privacy attitudes.

\subsection{Focus Group}
We conducted a one-hour focus group to validate our design, gauge comprehension, and measure fatigue. The focus group began with participants taking the survey. Afterward, we asked participants to give feedback on the format and the content, noting any instructions or questions that were unclear. The focus group concluded with a discussion of possible benefits and risks of wearable devices, in order to brainstorm any additional scenarios to include. Finally, we compensated participants with \$30 in cash. We recruited all of our focus group participants from Craigslist. Of the 13 participants, 54\% were female, and ages ranged from 18 to 64 (mu = 36.1, sigma = 15.3).  Education backgrounds ranged from high school to doctorate degrees, and professions included student, artist, marketer, and court psychologist.

\subsection{Recruitment and Analysis Method}
We recruited 2,250 participants August 7th-13th 2014 via Amazon's Mechanical Turk. We restricted participants to those over 18, living in the United States, and having a successful HIT completion rate of 95\% or above. Based on incorrect responses to either of the two comprehension questions, we filtered out 366 (16\% of 2,250) participants. We filtered out an additional 99 participants (4\% of 2,250) due to incomplete responses, and one participant who was under 18, leaving us with a total sample size of 1,784. Of these, 55.10\% were male, with a median age of 29 ($\sigma$ = 10.37).

In performing our analysis in the next section, we chose to focus on the very upset rate (VUR) of each scenario.  The VUR is defined as the percentage of participants who reported a `5' on the Likert scales. 
We use the VURs rather than the average of all Likert scores for the same reasons as Felt {\it et al.}: the VUR does not presume that the ratings, ranging from ``indifferent'' to ``very upset,'' are linearly spaced. Additionally, most were be upset, at least a little, in all scenarios when a device takes action without permission (rating distribution: ``1''= 455, ``2'' = 523, ``3'' = 902, ``4''' = 1,746, ``5'' = 6,654). Thus, the main distinguishing factor of a participant reacting to a given scenario is whether they were maximally upset or not, rather than how upset they were.

In this section, we followed Fischhoff {\it et al.}'s methodology and did not normalize the numerical responses. Rather, we report medians and quartiles, which are not impacted by outliers. For the open-ended question at the end (i.e., additional privacy concerns), two researchers independently coded 1,784 responses, with an initial agreement rate of 89.7\%. The researchers discussed and resolved any disagreements so that the final codings reflect unanimous agreement.

%%%%%%%%%%%%%%%%%%%

@@

\subsection{Risk and Benefit Rankings} 
\begin{figure}[t]
	\centering
	\includegraphics[width=0.47\textwidth]{riskbenefit.pdf}
	\caption{Participants' median risk-benefit ratings of technologies examined by Fischhoff \etal\cite{Fischhoff}, which we used for calibration, alongside familiar technologies (e.g., laptops, the Internet, etc.), wearable technologies, as well as two specific wearable devices (Google Glass and the Cubetastic3000).}
	\label{fig:techplot}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%

\section{Discussion}
Here, we discuss complementary future research directions in fields of privacy, ubiquitous computing, and user studies, along with specific limitations of this survey.

\subsection{Future Research Directions}
Wearables are still in infancy. Perceptions of situations and capabilities will change rapidly with advancements and increased exposure. However, videos and textual information are considered to be significantly sensitive by our participants, along with past participants of smartphone user perception studies. Various systems which detect and take actions for sensitive objects in photos and videos will be critical as wearables and other devices become more ubiquitous.

While privacy and security concerns were expected, consider these self-reported concerns as inspiration for future research: the high financial costs of wearables, health concerns from constant use, safety issues related to operation, any social impacts of use, and improving device aesthetics.

\subsection{Limitations}
One of the main limitations of this work is that our participants might not have interest,or an accurate idea of wearables and their capabilities. 83\% of our participants reported that they do not own a wearable device, but at this time, about 15\% of the general population own and use wearable devices \cite{Nilsen,WearableStatNews}, which makes our study reflective of the status quo. We believed that getting a representative survey base was a useful endeavor, although we could have easily recruited only wearables owners or people specifically interested in wearables. However, that will also have its own biases and limitations, since this does not reflect the general population. We expect user perceptions to change as rapidly as wearable technologies and the rate of adoption change.

\section{Related Work}
In this section, we discuss related work that has examined users' perceptions surrounding security and privacy risks.

\subsection{Ubiquitous Sensing}
Many authors have emphasized that we are rapidly moving towards a world of ubiquitous sensing and data capture, with ensuing privacy challenges~\cite{abowd2000charting,palen2003unpacking,camp2000internet}. Many researchers have worked to study how privacy can be preserved in such a future. Examples of such efforts include frameworks to design for privacy~\cite{bellotti1993design,camp2003designing,langheinrich2001privacy} or evaluate privacy~\cite{scholtz2004toward} in ubiquitous computing applications. Others have suggested various models for understanding privacy in ubiquitous computing systems~\cite{hong2004privacy, jiang2002approximate}.
However, none of these works attempted to quantify or rank user concern over different privacy risks.

\subsection{Smartphones and Wearables Concerns}
Many researchers have attempted to study end-user concerns about security or privacy issues associated with their smartphones~\cite{chin2012measuring, palen2000going, felt2012android}.

Recently Denning et. al studied privacy concerns bystanders have when others around them are wearing a wearable device~\cite{Denning2014}. Participants in their study expressed concerns due to the nature of wearables (subtle UI and potenitally ubiquitous). While their research examined the privacy concerns of bystanders in the presence of wearables, we are aware of no work that has looked at the privacy concerns of owners.

\subsection{User Perceptions and Behaviors}
In this paper we focus on measuring people's perceptions of security and privacy risks.
One limitation of user perceptions is that people don't always have enough information to make privacy-sensitive decisions; even if they do, they often trade off long-term privacy for short-term benefits~\cite{acquisti2005privacy}. Also, actual behavior may deviate from self-reported behaviors~\cite{jensen2005privacy} and privacy preferences~\cite{spiekermann2001privacy}.

%The survey was constructed in a way to randomize the order of the particular sets of questions participants saw, except for the open-ended question, which was always near the end of the survey, asked along with the demographics. For this reason, people were heavily primed for the open-ended question. However, this question was always shown before the IUIPC questions, so our results on privacy being the top concern isn't because of the bias from the privacy index. The intent of the open-ended question  was more to get a sense of what people were concerned of, and we believe the results do reflect their actual concerns, but with a bit more clarity, since the participants were already thinking about such risks related to wearables.

%%%%%%%%%%%%%%%%%%%

\section{Conclusion}

We surveyed 2,250 internet users to determine what contributes to a violation of privacy or security, which technologies are risky, and what users think are the biggest risk for operating wearable devices. Participants how upset they would be if 304 situations occurred, assessed the risk and benefit for 20 new technologies, and gave open-ended responses to express their concerns. We provide insight into how much and why data, recipient, and device contribute to users' perception of a situation, calibrate answers with existing smartphone literature, and provide a regression model. An assessment of a range of new technologies shows that users perceive new technologies to be low-risk and low-benefit, but we suspect this is due to limited exposure that an average person has with wearables techology. We also state what users perceived as the most significant concerns with respect to wearable devices. We conclude by discussing future research directions in the wearables and user study space.

%NOTE: RESEARCH ETHICS/ ACKS COMMENTED OUT FOR ANONYMITY

%\section{Research Ethics} 
%We received advance approval from University of California, Berkeley's Institutional Review Board to perform this user study. Survey data was collected in an anonymous manner. Although the focus group was not conducted in an anonymous manner, participants were not asked to offer any confidential or sensitive information.

%\section{Acknowledgments}
%The authors would like to thank The National Science Foundation's Graduate Research Fellowships Program (NSF GRFP), and the Intel Science and Technology Center for Secure Computing (also known as  Secure Computing Research for Users' Benefit, SCRUB), for the support of this research. Inspiration for this work emerged out of fruitful discussions at the Berkeley Laboratory for Usable and Experimental Security (BLUES) meetings. Many thanks go out to the many generous colleagues who have provided feedback and encouragement.

%%%%%%%%%%%%%%%%%%%
%%%            BIB & ACKS          %%%
%%%%%%%%%%%%%%%%%%%

\bibliographystyle{abbrv}
\bibliography{wearables_survey}  % wearables_survey.bib is the name of the Bibliography

%APPENDICES are optional
%\balancecolumns
\appendix
%Appendix A
\section{Fischhoff Prompts}
\label{sec:prompt}

\textit{We would like to ask you to rate the <risks/benefits> associated with each of the following technologies.}

{\bf Risks:} \textit{Consider all types of risks: the risk of physical harm or death, the risk to others or bystanders, the financial cost of the technology, any distress caused by the technology, what the consequences would be if the technology was misused, any impact on the public, work, or personal life, and other considerations. (e.g. for electricity, consider the risk of electrocution, the pollution caused by coal, the risk that miners need to take to mine the coal, the cost to build the infrastructure to deliver electricity, etc.) Give a global estimate over a long period of time (say, a year) of both intangible and tangible risks.} \\[-.6cm]

\textit{Do not consider the costs or risks associated with these items. It is true, for example, that sometimes swimmers can drown. But evaluating such risks is not your present job. Your job is to assess the gross benefits, not the net benefits which remain after the costs and risks are subtracted out.} \\[-.6cm]

\textit{Please rate the following technologies below with a number. We know that this might be a bit hard to do, but please try to be as accurate as possible, adjusting the numbers until they feel they are right for you. Start with the least risky technology at 10 and assign higher numbers for the more risky technologies. (For instance, a technology rated 14 is half as risky as a technology rated 28.)}

{\bf Benefits:} \textit{Consider all types of benefits: how many jobs are created, how much money is generated directly or indirectly, how much enjoyment is brought to people, how much a contribution is made to the people's health and welfare, what this technology promotes, and so on. (e.g. for swimming, consider the manufacture and sale of swimsuits, the time spent exercising, the social interactions during swimming, and the sport created around the activity.) Give a global estimate over a long period of time (say, a year) of both intangible and tangible benefits.} \\[-.6cm]

\textit{Do not consider the costs or benefits associated with these items. It is true, for example, that electricity also creates a market for home appliances. But evaluating such benefits is not your present job. Your job is to assess the gross risks, not the net risks which remain after the costs and risks are subtracted out.} \\[-.6cm]

\textit{Please rate the following technologies below with a number. We know that this might be a bit hard to do, but please try to be as accurate as possible, adjusting the numbers until they feel they are right for you. Start with the least beneficial technology at 10 and assign higher numbers for the more beneficial technologies. (For instance, a technology rated 34 is twice as beneficial as a technology rated 17.)}

%\section{Risk and Benefit Rankings}
%\label{sec:techrank}
%
%BENEFIT: 
%
%technology 	median	25\%		75\% \\
%electricity	87	50	100\\
%internet	65	45	100\\
%laptops	60	40	80\\
%email	50	30	75\\
%smartphones	50	32.5	75\\
%location tracking	40	20	67.5\\
%heart rate detection	40	28	62.5\\
%language detection	35	15	60\\
%voice recognition	25	15	40\\
%speech to text	25	15	36.25\\
%lawnmowers	24	15	40\\
%facial recognition	22	13	40\\
%guns	20	10	30\\
%motrocycles	20	12	40\\
%voice based emotion detection	20	10	30\\
%facial detection	20	10	32\\
%discrete camera	20	15	30\\
%smartwatches	20	10	32.5\\
%google glass	20	12	40\\
%fitness trackers	19	10	30\\
%cubetastic	18	10	30\\
%discrete microphone	15	10	20\\
%age detection	12	10	21\\
%gender detection	10	10	15
%
%RISK: 
%
%technology 	median	25\%		75\%\\
%guns	60	40	80\\
%motrocycles	45	27	70\\
%electricity	25	15	40\\
%lawnmowers	20	12	30\\
%facial recognition	17	12.5	30\\
%internet	15	10	30\\
%discrete camera	12	10	30\\
%location tracking	10	10	20\\
%age detection	10	10	15\\
%gender detection	10	10	12\\
%language detection	10	10	10\\
%voice based emotion detection	10	10	15\\
%facial detection	10	10	25\\
%voice recognition	10	10	15\\
%heart rate detection	10	10	10\\
%email	10	10	16\\
%speech to text	10	10	10\\
%discrete microphone	10	10	20\\
%smartphones	10	10	19\\
%laptops	10	10	15\\
%fitness trackers	10	10	10\\
%smartwatches	10	10	10\\
%google glass	10	10	20\\
%cubetastic	10	10	30

%\section{Coding Label Definitions}
%\label{sec:coding}
%
%Privacy: ``privacy,'' revealing personal information, spying. \\
%Security:  ``security,'' compromise, malware, hacking. \\
%GPS tracking: ``location,'' ``GPS,'' being monitored. 
%
%Unaware use: using data without permission or in a different way than understood by user. \\
%Unaware collection: collecting data without permission. \\
%Unaware access: disclosure of data without permission. \\
%False information: inaccurate or maliciously false data.
%
%Health Risk: radiation, cancer, or long-term effects.\\
%Safety: distractions causing car crashes or injuries, mugging or violence because of the device, injuries from device malfunctions (battery burns).\\
%Discomfort: eye strain, headache, obscured vision, irritation. \\
%Financial cost: getting ripped off by buying the device or device accessories, having to buy another device when broken or stolen, financial compromise caused by device. \\
%Theft: the device getting stolen. 
%
%Social Impact: dependency, distance from friends and family, changes in decision making, social changes, etc. \\
%Social Stigma: judgment, hate, or bystander discomfort.\\ 
%Aesthetics: fashion, the device being ugly, mentions of not looking cool/dorky. 
%
%Miscellaneous: odd comments, uncommon concerns. \\
%None: ``None,'' no threat, perceiving no big concerns \\
%Don't know: ``do not know,'' hinting at confusion \\
%Don't care: `` do not care,'' nonchalant answers

%\section{Detailed Tech Rankings}

\balancecolumns

% That's all folks!
\end{document}
\\

>>>>

@@

\subsection{Risk and Benefit Rankings} 
\begin{figure}[t]
	\centering
	\includegraphics[width=0.47\textwidth]{images/riskbenefit.pdf}
	\caption{Participants' median risk-benefit ratings of technologies examined by Fischhoff \etal\cite{Fischhoff}, which we used for calibration, alongside familiar technologies (e.g., laptops, the Internet, etc.), wearable technologies, as well as two specific wearable devices (Google Glass and the Cubetastic3000).}
	\label{fig:techplot}
\end{figure}

@@
